Current State of Knowledge Representation Systems for Robotics

### 2011-12-12 krs-survey.tex
Added most of the 'scenario' section

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A taxonomy of features of knowledge representation systems}
\label{sect|features}

@@

\subsubsection{Representation of uncertainty}

@@

\subsubsection{Spatio-Temporal Representations}

>>>>

\fxnote{Add nice illustrations from MORSE}

In order to illustrate what we consider to be the required features of a
knowledge representation system for robotics, we propose the following
scenario.

While devising a scenario inevitably constraints the breadth of abilities we
examine to the ones actually needed for this specific scenario, we insist on
the fact that our main purpose is to demonstrate on a real case what
representational features are desirable.

We entitle our scenario ``the Brownie scenario''.

Robi and Roba are two service robots. They are considered to be able to freely
move and pick objects, but they are not expected to have the exact same
hardware and softwares architectures, and especially, they are not expected to
have the same knowledge representation system. These robots cooperate with a
human in a kitchen environment.

The main task of the scenario is the joint realization of a brownie, that
starts with the human injunction ``Let's make a brownie for tonight!''.

The scenario is successful if the task is achieved (the brownie is made) and:

	\item it took less time that it would have require for the human alone,

	\item it didn't require a heavier cognitive involvement from the human that
	what would have been required without the robots' help.

We voluntarily do not try to detail the subtasks of the scenario and to define
how they are shared amongst agents. In our analysis we focus on the general,
\textit{a priori} representational needs of the scenario.

A ``first-order'' analysis of this task leads to a first list of categories of
required features:

\begin{enumerate}

	\item Representation abilities related to the execution of a complex
	spatio-temporal task,

	\item Representation abilities related to cooperation with other agents.

\end{enumerate}

% Representation of a complex task
The first category can be further refined: to prepare and bake a brownie, the
robot first needs to make sense of the very term \emph{brownie}: what is it?
what is it used for? what is it made of? etc. We call this knowledge
\emph{common-sense knowledge} and the robot must be able not only to represent
it, but also to have some kind of access to it (for instance through a initial
set of facts that are made available at startup, or via access to a Web-based
knowledge base like Wikipedia, etc.)

In conjunction with the representation of the action \emph{make} (and it's
possibly attached common-knowledge), this should lead the robot to build and
represent a \emph{context}: we are in a scenario involving cooking. Actions
related to cooking often take place in the kitchen, cooking requires ingredients, 
utensils and a procedure that may be provided by a recipe, etc.

This last sentence implies several other features for our knowledge
representation system: ``cooking often takes place in the kitchen'' implies
that representation of both uncertainty and likelihood is desirable. The fact
that cooking is associated to a place further implies that the system models
locations and is able to attach \emph{thematic relations} to concept
(here, the likely location of the cooking action).

``cooking requires ingredients that may be provided by a recipe'' hints about a
very common feature available in most knowledge representation systems:
\emph{reasoning}. The robot \emph{infers} that cooking may require a recipe
since a list of ingredients is a pre-requisite of the cooking action, and a
recipe may provided such a list. If we omit the ``may'', this is a typical
example of first-order logic reasoning. Many other reasoning techniques exist
(including probabilistic ones -- ones able to deal with the ``may''), we shall
illustrate some of them further in this scenario.

As mentioned, a recipe often provides a procedure (or a \emph{plan}). The robot
should be able to store this plan in a way that allow later execution.  The
plan is likely to contain \emph{spatio-temporal constraints} (like ``put
the brownie in the oven for 20 min'') that must as well be appropriately
represented.

Moreover, procedures are often \emph{underspecified}: we can expect the recipe
to provide a cooking duration, but we usually do not expect the recipe to tell
us to first open the oven door, and then put the cake into it, since it is
self-evident that the door must first be opened. Such underspecification should
be detectable, representable, and ideally completable by the knowledge
representation system.

Besides representation of space and time, we may have

% Representation feature that enable cooperation
Then, we want our three agents to cooperate. This, in turn, leads to a very
different set of cognitive abilities.

Cooperation in our scenario can intervene at many levels: for instance, an
agent may want to inform another one about the number of eggs that are
necessary for the brownie. It makes sense to help in this way only if the first
agent knows that the recipient agent both needs the information and does not
know it. This in turn requires the robot to be able to model the knowledge of
the other agents: to think \emph{from the perspective} of another agent (this
idea is related to the so-called Theory of Mind~\cite{...}).

Ability to communicate is one important pre-requisite to collaboration.
Communication in general~\cite{Jakobson} requires the addresser and the
addressee to share a common interpretative framework (shared common-sense
knowledge -- or cultural background -- and a shared context). In our scenario,
the agents are working in a kitchen. This element of context does not however
suffice if, for example, an agent asks another agent to ``give {[him]} the
bowl''. Besides the symbol ``bowl'', which physical entity are we actually
talking about? If we want to act on the world, this \emph{grounding} operation
is essential, and may be tightly bound to the underlying knowledge
representation system. Note that grounding usually denotes the {\it top-down}
operation: from the symbol to the percept. It is however commonly bundled with
the converse operation, that retrieve (or create) symbols from perception.

A related ability is called \emph{pre-supposition accomodation}: if one of the
agent moves behind another one, with the brownie dough in its arm, and says
``be careful, I'm behind you!'', we want the first agent to be able to
represent both symbolically and geometrically (because, for instance, if the
agent want to move, it must take into account the new obstacle) something that
was not directly perceived. A knowledge representation system may be able to
provide structures to represent and reason about such cases.

Also central to cooperation are the notions of \emph{joint
intentions} and \emph{joint goals}~\cite{Tomasello2005, Bratman2009}: to help
the human during the cooking session, the robots need to store at least how far
they are into the recipe, what is the next step the human is likely to go for,
how task are currently split between agents, what action is currently
blocking the procedure, etc. This knowledge should let the robot identify the
intentions of other agents and create accordingly joint goals. Hence, a
knowledge representation system aiming at dealing with cooperative behaviours
is likely to have goal management structures taking explicitly into account
other agents' actions and goals.

In order to effectively share tasks, the robot must also know what it is
capable of: \emph{capability introspection} (both in term of general capability
and of immediate ability) is thus often desirable. More general introspection
(like the ability to tell ``who I am'' or ``what do I think of'' does not
appear to be necessary in our scenario. This may however enrich the human-robot
interaction.

Last but not least, our scenario assumes implicitly \emph{natural interaction}
between humans and robots (as showed by the casual style of the
order ``Let's make a brownie!''). While natural language processing {\it
per-se} is usually out of the scope of a knowledge representation system, we
may want to be sure these systems successfully interoperate, \ie that the
knowledge representation system provides efficient support to the natural
language processing module (for instance by adopting models and vocabulary that
are both well suited for machine processing and remain as close as possible to
the humans own structures and vocabulary).

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A typology of features of knowledge representation systems}
\label{sect|features}

The previous section detailed an imaginary cooking scenario. We identified, in
no particular order, numerous desirable features for a knowledge representation
system for robotics.

This section proposes a more formal typology of desirable features for a such a
system. For each feature, we provide a short definition along with links to
relevant literature.

@@

\subsubsection{Representation of uncertainty and likelihood}

@@

\subsubsection{Role Representations}

Spatio-Temporal Representations:
